Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-03-11 analysis/paper/paper.Rmd
revision in progress

---
title: "Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
    equal_contributor: "yes"
    orcid_id: 0000-0001-7875-9015
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
    equal_contributor: "yes"
  - name: David Lapins
    email: david.lapins@pc.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Kyle Lochhead
    email: Kyle.Lochhead@gov.bc.ca
    institute: [FLNR]
    correspondence: false
  - name: Gregory Paradis
    email: gregory.paradis@ubc.ca
    institute: [UBC]
    correspondence: false

@@

tsa <- tm_shape(tsaCost, name = "Cost")+
  tm_raster(style = "cont", title = "Cost")+
  tm_shape(st_union(tsaBoundary))+
  tm_borders(col = "black")+
  tm_compass(position = c(0.3, 0.11), size = 1)+
  tm_scale_bar(position = c("center", "bottom"), text.size = 1)+
  tm_layout(legend.position = c("left", "bottom"),
            legend.bg.color = "white")

@@

library(dplyr)
library(sf)
library(roads)
library(terra)
library(tmap)
library(purrr)
library(caribouMetrics)
library(pfocal)

@@

allMaps <- purrr::map(
  1:nrow(allProj),
  ~ qtm(tsaCost, raster.style = "cont", raster.palette = "Greys",
        raster.alpha = 0.5, raster.title = "Cost")+
    qtm(cutblocks, fill = NULL, borders = "grey40", borders.lwd = 1.5)+
    qtm(roads, lines.col = "red", lines.lwd = 2)+
    qtm(read_sf(here(allProj$output[[.x]])), lines.col = "yellow", lines.lwd = 2)+
    qtm(exRoads, lines.col = "black", lines.lwd = 2)+
    tm_layout(legend.show = .x == nrow(allProj),
              legend.only = .x == nrow(allProj),
              main.title = allProj$mapTitle[[.x]],
              main.title.size = 0.75))

allMaps[[nrow(allProj)]] <- allMaps[[nrow(allProj)]]+
  tm_add_legend(type = "line", 
                labels = c("Existing roads", "Projected roads", "Observed roads"),
                col = c("black", "yellow", "red"))+
    tm_add_legend(type = "fill", 
                labels = "Cutblocks",
                col = NA, border.col = "grey40")+
  tm_layout(legend.only = TRUE, legend.position = c("center", "center"))

>>>>

---
title: "Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
    equal_contributor: "yes"
    orcid_id: 0000-0001-7875-9015
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
    equal_contributor: "yes"
  - name: David Lapins
    email: david.lapins@pc.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Gregory Paradis
    email: gregory.paradis@ubc.ca
    institute: [UBC]
    correspondence: false
  - name: Kyle Lochhead
    email: Kyle.Lochhead@gov.bc.ca
    institute: [FLNR]
    correspondence: false

@@

tsa <- tm_shape(tsaCost, name = "Cost")+
  tm_raster(style = "cont", title = "Cost",palette="Greys")+
  tm_shape(st_union(tsaBoundary))+
  tm_borders(col = "black")+
  tm_compass(position = c(0.3, 0.11), size = 1)+
  tm_scale_bar(position = c("center", "bottom"), text.size = 1)+
  tm_layout(legend.position = c("left", "bottom"),
            legend.bg.color = "white")

@@

library(dplyr)
library(sf)
library(roads)
library(terra)
library(tmap)
library(purrr)
library(caribouMetrics)
#library(pfocal)

@@

allMaps <- purrr::map(
  1:nrow(allProj),
  ~ qtm(cutblocks, borders = "#92c5de", fill="#92c5de", borders.lwd = 1,)+
    qtm(tsaCost, raster.style = "cont", raster.palette = "Greys",
        raster.alpha = 0.25, raster.title = "Cost")+
    qtm(roads, lines.col = "#0571b0", lines.lwd = 2,lines.lty="solid")+
    qtm(read_sf(here(allProj$output[[.x]])), lines.col = "#ca0020", lines.lwd = 2)+
    qtm(exRoads, lines.col = "black", lines.lwd = 2)+
    tm_layout(legend.show = .x == nrow(allProj),
              legend.only = .x == nrow(allProj),
              main.title = allProj$mapTitle[[.x]],
              main.title.size = 0.75))

allMaps[[nrow(allProj)]] <- allMaps[[nrow(allProj)]]+
  tm_add_legend(type = "line", 
                labels = c("Existing roads", "Projected roads", "Observed roads"),
                col = c("black", "#ca0020", "#0571b0"),lty=c("solid","solid","solid"))+
    tm_add_legend(type = "fill", 
                labels = "Cutblocks",
                col = "#92c5de", border.col ="#92c5de")+
  tm_layout(legend.only = TRUE, legend.position = c("center", "center"))
